---
title: "DataScience_hm5"
author: "KaiYu He(kh3074)"
date: "11/16/2021"
output: html_document
---
```{r}
library(tidyverse)
```

# Problem 1  
```{r}
homicide_df = 
  read_csv("data/homicide-data.csv",na = c("","Unkonw")) %>%
  mutate(
    city_state = str_c(city,",",state),
    resolution = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest" ~ "unsolved",
      disposition == "Closed by arrest" ~ "solved"
    )) %>%
  relocate(city_state)%>%
  filter(city_state != "Tusla,AL")
homicide_df%>%count(city_state)
```

Let's focus on Baltimore,MD.
```{r}
baltimore_df = 
  homicide_df%>%
  filter(city_state == "Baltimore,MD")

baltimore_summary = 
  baltimore_df%>%
  summarize(
    unsolved = sum(resolution == "unsolved"),
    n = n()
  )

baltimore_test = 
  prop.test(
  x = baltimore_summary%>%pull(unsolved),
  n = baltimore_summary%>%pull(n)
  )

baltimore_test %>%
  broom::tidy()
```

let's try to iterate across cities!
First off, write a function.
```{r}
prop_test_function = function(city_df)
  {
  city_summary = 
  city_df%>%
  summarize(
    unsolved = sum(resolution == "unsolved"),
    n = n()
  )

city_test = 
  prop.test(
  x = city_summary%>%pull(unsolved),
  n = city_summary%>%pull(n)
  )
  }
```

Now, let's iterate across all cities.
```{r}
results_df =
  homicide_df%>%
  nest(data = uid:resolution)%>%
  mutate(
    test_result = map(data,prop_test_function),
    tidy_result = map(test_result,broom::tidy)
  )%>%
  select(city_state,tidy_result)%>%
  unnest(tidy_result)%>%
  select(city_state,estimate,starts_with("conf"))
results_df

```

Try to make a plot showing estimates and confidence intervals.

```{r}
results_df%>%
  filter(city_state!="Tulsa,AL")%>%
  mutate(city_state = fct_reorder(city_state,estimate))%>%
  ggplot(aes(x = city_state,y = estimate))+
  geom_point()+
  geom_errorbar(aes(ymin = conf.low,ymax = conf.high))+
  theme(axis.text.x = element_text(angle = 90,vjust = 0.5,hjust = 1))
```



# Problem 2

### Create a tidy dataframe

Method_1 using a for loop.
```{r message=FALSE}
data_raw = tibble() # Create an empty data frame
Arm = c("exp","con")
Id = str_pad(string = 1:10,width = 2,side = 'left',pad = '0')
for (id in Id){
  for (arm in Arm){
    arm_id = 
      read_csv(str_c("data/Problem_2_data/",arm,"_",id,".csv")) %>%
      mutate(id = id,arm = arm)%>%
      relocate(arm,id)
    data_raw = bind_rows(data_raw,arm_id)
  }
}
```
```{r}
data_tidy = 
  data_raw%>%
  janitor::clean_names()%>%
  pivot_longer(week_1:week_8,
              names_to = 'week',
              values_to = 'data')%>%
  mutate(subject = str_c(arm,id))%>%
  select(subject,week,data)%>%
  pivot_wider(names_from = subject,values_from = data)%>%
  mutate(week = as.numeric(str_remove(week,"week_")))
data_tidy
```

Method_2 using purrr package
```{r, message=FALSE}
data_raw = 
  tibble(
  file_names = list.files(path = "data/Problem_2_data/")
)%>%
  mutate(file_names = str_c("data/Problem_2_data/",file_names))%>%
  mutate(data = map(file_names,read_csv))%>%
  unnest(data)%>%
  mutate(
    file_names = str_remove(file_names,"data/Problem_2_data/"),
    file_names = str_remove(file_names,".csv")
    )%>%
  separate(file_names,into = c("arm","id"),sep = '_')
```
```{r}
data_tidy = 
  data_raw%>%
  janitor::clean_names()%>%
  pivot_longer(week_1:week_8,
              names_to = 'week',
              values_to = 'data')%>%
  mutate(subject = str_c(arm,id))%>%
  select(subject,week,data)%>%
  pivot_wider(names_from = subject,values_from = data)%>%
  mutate(week = as.numeric(str_remove(week,"week_")))
data_tidy
```

### Spaghetti plot

```{r}
data_tidy%>%
  pivot_longer(con01:exp10,
               names_to = 'subject',
               values_to = 'data')%>%
  ggplot(aes(x = week,y = data,color = subject))+
  geom_line()
```
To see the difference between control group and experiement we nee to draw a plot seperated by group. 

```{r}
data_tidy%>%
  pivot_longer(con01:exp10,
               names_to = 'subject',
               values_to = 'data')%>%
  mutate(arm = substr(subject,1,3))%>%
  ggplot(aes(x = week,y = data,group = subject))+
  geom_line(aes(color = arm))
```

- From the grouped line plot we can conclude that the value of experiment group is greater than contorl group.

# Problem 3

### Introduce data
```{r}
set.seed(10)
iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species))

iris_with_missing = 
  iris_with_missing%>%
  janitor::clean_names()
iris_with_missing
```

```{r}
fill_missing = function(vector){
  if(typeof(vector[1])=="double"){
  mean = round(mean(vector,na.rm = TRUE),2)
  vector[is.na(vector)] = mean
  round(vector,2)
  vector
  }
  else {
    vector[is.na(vector)] = "virginica"
    vector
  }
}
iris_with_missing %>%
  map(fill_missing)
```




